---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

#gglyr

Abstraction of mapping layers in ggplot2 for quick creation of high quality maps.

## Set library path and view library layers

```{r}
library(tidyverse)
library(sf)
library(gglyr)
# Set gglyr library - this can be relative or absolute path. No support for URLs yet
gglyr_set_lib('c:/gglyr_lib')
# Testing retrieving currently set lib
gglyr_get_lib()
# Can list all the layers in the current lib
gglyr_list_lyrs()
```
## Create and add a layer to the library

```{r}
# Load spatial data from remote URL
dist_from_shore <- geojsonsf::geojson_sf('https://services1.arcgis.com/RbMX0mRVOFNTdLzd/arcgis/rest/services/MaineDMR_Distance_From_Shore/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson')
dist_from_shore <- dist_from_shore %>%
  dplyr::select(distance = Waters, zone = Zone, geometry)

# Make a ggproto and save it with gglyr_save
geom_sf(data = dist_from_shore, fill = NA, color = 'grey', inherit.aes = F) %>%
  gglyr_save(., 'maine_zone_dist_no_ol',
           'Maine lobster zones/distance from shore intersection with no overlaps, overlaps as zone C/D etc.')
```

## Load a layer from the library

```{r}
ggplot() +
  gglyr('maine_zone_dist_no_ol')
```
Data can be extracted from ggproto back to SF object if needed:

```{r}
proto <- gglyr('maine_zone_dist_no_ol')
distance <- proto[[1]]$data
class(distance)
```
## Multiple layers stacked

Can save multiple ggplot layers together as a list, ie, these layers were loaded from boundaries.Rda as SF objects - to make it easier to edit layer aesthetics, pass list names (vs numeric indices if none present).

```{r}
load('boundaries.Rda')

list(
  '3NM' = geom_sf(data = three_nm, color = 'darkorchid4', inherit.aes = F),
  '12NM' = geom_sf(data = twelve_nm, color = 'darkred', inherit.aes = F),
  '24NM' = geom_sf(data = twenty_four_nm, color = 'darkgreen', inherit.aes = F),
  'EEZ' = geom_sf(data = eez, color = 'grey', linetype = '21', inherit.aes = F)
) %>%
  gglyr_save(., 'maine_nm_lines', 'Maine 3NM line with US 12, 24NM lines and EEZ')

ggplot() +
  gglyr('ne_coast') +
  gglyr('maine_nm_lines') +
  coord_sf(xlim = c(-72, -67), ylim = c(42, 45))

```

## Retrieve comment from layer

```{r}
# Can retrieve comment from layer by passing verbose = T
gglyr('gom_bathy', verbose = T)
```

## Zoom a ggplot to the bounds of an SF layer

`gg_bound_sf(sf_layer)`


## Make nice maps quickly

```{r}
ggplot() +
  gglyr('gom_bathy') +
  gglyr('ne_coast') +
  gglyr('maine_zone_dist_no_ol') +
  gglyr('maine_nm_lines') +
  # Bound it to outline of distance to shore
  gg_bound_sf(distance) +
  labs(x = 'Longitude', y = 'Latitude')
```


## What if the source spatial data changes??

If the source spatial data changes or is updated, right a function to retrieve the data from the source file or URL and return a `ggproto`. The function can receive additional arguments, ie:

```{r}
random_maine_points <- function(points) {
  lats <- runif(points, min = 43, max = 45)
  lons <- runif(points, min = -70, max = -67)
  points <- data.frame(lat = lats, lon = lons) %>%
    st_as_sf(coords = c('lon', 'lat'), crs = 4326)
  p <- geom_sf(data = points, color = 'red', size = 2)
  return(p)
}

gglyr_save(random_maine_points, 'random_points', 'Generate random points off Maine.')


ggplot() +
  gglyr('ne_coast') +
  gglyr('random_points', points = 15) +
  gg_bound_sf(distance) +
  labs('15 Random Points')
  
ggplot() +
  gglyr('ne_coast') +
  gglyr('random_points', points = 100) +
  gg_bound_sf(distance) +
  labs('100 Random Points')


```









